The Revisited Hidden Weight Bit Function

### 2025-03-26 RevisedHiddenWeight.tex
draft answer

@@

\begin{proof}[Proof of Proposition~\ref{proposition:dtn}]
    By considering binary vectors $x\in\F_2^n$ as $x=(y,z)$ with $y\in\F_2^{2t}$ and $z\in\F_2^{n-2t}$, we get:	
	\begin{align*}
		\Dtkna{t}{k}{n}{a}&=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,n}(x)+a \cdot x}\\
		&=\sum_{(y,z)\in\Ekn{k}{n}} (-1)^{d_{t,2t}(y)+b \cdot y +c \cdot z}\\
		&=\sum_{\ell=0}^{2t} \sum_{\substack{y \in \Ekn{\ell}{2t}\\z \in \Ekn{k-\ell}{n-2t}}} (-1)^{d_{t,2t}(y)+b \cdot y +c \cdot z}\\
		&=\sum_{\ell=0}^{2t}\left(\sum_{y \in \Ekn{\ell}{2t}} (-1)^{d_{2t}(y)+b \cdot y}\right)\left( \sum_{z \in \Ekn{k-\ell}{n-2t}} (-1)^{c \cdot z}\right)\\&=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b}\cdot\kraw{k-\ell}{\w(c)}{n-2t}.\qedhere
	\end{align*}
\end{proof}

>>>>

\pmnote{For example, the filter functions leading to the best current performances for FiLIP in HHE~\cite{CCS:CDPP22,CIC:MeaParPei24,eprint:AGHM24} are xor-threshold functions, the direct sum of a $k$-variable linear function and an $m$-variable function giving $1$ if and only if the input has Hamming weight at least a threshold $d$ (which generalizes the majority function). Using Proposition $7$ in~\cite{IEEE:CarMea21}, the nonlinearity of a xor-threshold function is at most:
\[2^{n-1}-2^k \cdot M \text{ where }
M=\left\{\begin{array}{ll}
\binom{m-1}{\frac{m-1}{2}}&\text{ if }m\equiv 1\bmod 2,\\
\frac{1}{2} \binom{m}{\frac{m}{2}}&\text{ if }m\equiv 0\bmod 2.\\
\end{array}\right.
\]
The nonlinearity of this whole family of functions is similar to the one of the majority, hence the revisited HWBF provides a better nonlinearity that currently used filters for FiLIP for the same sizes, allowing to thwart correlation-like attacks with functions in less variables.}

@@

\begin{proof}[Proof of Proposition~\ref{proposition:dtn}]
    By considering binary vectors $x\in\F_2^n$ as $x=(y,z)$ with $y\in\F_2^{2t}$ and $z\in\F_2^{n-2t}$, we get:	
	\begin{align*}^
		\Dtkna{t}{k}{n}{a}&=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,n}(x)+a \cdot x}\\
		&=\sum_{(y,z)\in\Ekn{k}{n}} (-1)^{d_{t,2t}(y)+b \cdot y +c \cdot z}\\
		&=\sum_{\ell=0}^{2t} \sum_{\substack{y \in \Ekn{\ell}{2t}\\z \in \Ekn{k-\ell}{n-2t}}} (-1)^{d_{t,2t}(y)+b \cdot y +c \cdot z}\\
		&=\sum_{\ell=0}^{2t}\left(\sum_{y \in \Ekn{\ell}{2t}} (-1)^{d_{2t}(y)+b \cdot y}\right)\left( \sum_{z \in \Ekn{k-\ell}{n-2t}} (-1)^{c \cdot z}\right)\\&=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b}\cdot\kraw{k-\ell}{\w(c)}{n-2t}.\qedhere
	\end{align*}
\end{proof}
